\hspace{1cm} Do syntactic and semantic similarity lead to interference effects?\newline Evidence from self-paced reading and event-related potentials using German

### 2023-10-09 paper/main.tex
edited spr study

It is well-known \parencite[e.g., ][]{rayner2000effect} that the last word in a clause-final position causes a slowdown in reading; such a slowdown has the potential to spill over to the subsequent regions, possibly affecting the estimated effects at the pre-critical and critical regions. The spillover of longer reading times can be problematic because the standard deviation increases as well \parencite{wagenmakers2007linear}; such an increase in standard deviation would drastically lower statistical power. In order to attenuate spillover from the clause-final word in the embedded clause preceding the critical region, we inserted two adverbs. This way, the critical region will be less affected by the clause-boundary slowdown. This design also has the advantage that any potential effects seen at the pre-critical region (the adverb preceding the verb) are less likely to be due to spillover; it is important to look at the pre-critical region as previous work with this design found effects at the pre-critical region (we revisit this detail in the General discussion).

@@

\subsubsection{Self-paced reading times (Experiments 1a and 1b combined)}
Reading times across the whole sentence are shown in Figure \ref{fig:whole_sentence} A and B, separately for high and low syntactic interference because these conditions had partially different sentence structure. 
%\clearpage

@@

It is apparent from Figure \ref{fig:whole_sentence} A and B that, regardless of the syntactic manipulation  at the distractor, reading times between high and low semantic interference started to differ: distractors in the high semantic interference conditions induced longer reading times than in the low semantic interference conditions. This is probably due to encoding interference \citep{mertzen, jaeger_etal_2015_retrieval_encoding} and persisted in the following regions. Nonetheless, we refrained from analyzing the distractor and the immediately following regions, because they differed between conditions. Instead we focused our analyses on regions which were identical across conditions: The pre-critical, critical and spill-over region. Figure \ref{fig:whole_sentence} C shows the pooled reading times of these regions (and additionally the pre-pre-critical region which was identical across conditions as well, but might be confounded by spill-over from the syntactic manipulation). The pre-pre-critical and pre-critical region show longer reading times for high vs.\ low semantic interference conditions. The critical verb was read slowest when syntactic and semantic interference were both high and fastest when syntactic interference was high and semantic interference low. The other two conditions showed intermediate reading times. The spill-over region again primarily showed a difference between high and low semantic interference conditions.

Panel D shows the reading times of the critical and surrounding regions for each of the sub-parts of the SPR experiment. The sub-experiment with multiple sessions and items 1-60 (N = 204, left most sub-figure) showed results similar to the pooled results presented in Panel C. The sub-experiment with multiple sessions and items 61-120 (N = 160) showed a semantic interference effect at the critical verb and less clear results in the surrounding regions. Additionally, this sub-experiment showed shorter reading times compared to the other sub-experiments in general. This was probably caused by adaptation to the task, because the same participants had completed another session earlier. The sub-experiment with a single session and items 1-60 (N = 350) showed a semantic interference effect in all regions. The sub-experiment with a single session and items 61-120 (N = 220, right most sub-figure) showed a semantic interference effect in the regions surrounding the critical verb, but not at the verb itself. At the verb, reading times were longest when both syntactic and semantic interference were high. Reading times were a bit faster when both syntactic and semantic interference were low. The other two conditions (high syntactic/low semantic and low syntactic/high semantic) lead to the fastest verb reading times in this sub-experiment. These somewhat inconsistent results, especially in the critical region, across the sub-experiments and the random assignment of participants to the sub-experiments motivated us to gain estimates of the effects under investigation for the individual participants (see Figure \ref{fig:spr_individual}).

\begin{figure}[H]
    \caption{Individual estimates of syntactic and semantic interference and their interaction at the critical verb for all 774 participants in the self-paced reading experiment. Shown are shrunken estimates from a Bayesian hierarchical linear mixed model. Circles show individual’s mean effects, errors bars are 95\,\% credible intervals. The red dashed line shows an effect of zero (difference of zero milliseconds). Two solid red lines mark an effect size of 10 and 20 ms, respectively.}
    \label{fig:spr_individual}
    \centering
    \includegraphics[width=\textwidth]{images/individual_diffs.jpg}
\end{figure}

The individual-level effects were derived from a Bayesian linear mixed model with the priors shown in Table \ref{tab:spr_priors} with the intermediate slope prior of Normal(0, 0.05) and random slopes for syntactic and semantic interference and their interaction but without correlations of random effects.

Figure \ref{fig:spr_individual} shows that at the critical verb, the 95\,\% credible intervals for the syntactic interference effect of all participants were centered around zero. In contrast, participants consistently displayed a small effect of semantic interference with narrow 95\,\% credible intervals. The individual-level estimates of the interaction were a bit larger but they were associated with more uncertainty (wider 95\,\% credible intervals). The individual-level results help to understand the population-level posteriors presented in Figure \ref{fig:spr_posteriors} and the population-level Bayes factor analysis (see Figure \ref{fig:spr_bfs}).

The posteriors of the pre-critical, critical and spill-over regions were very similar (see Figure \ref{fig:spr_posteriors}). For the syntactic interference effect, they were close to zero in all regions. In contrast, for the semantic interference effect, the estimates ranged from 4 ms (lower bound in the critical region) to 14 ms (upper bound in the pre-critical region). The posteriors for the interaction were consistent with an interaction effect between 1 ms and 13 ms in the pre-critical and spill-over region. They were largest in the critical region (95\,\% CrI [7, 22 ms]).

\begin{figure}[H]
    \caption{Posteriors for the syntactic and semantic interference effects and their interaction at the critical verb and surrounding regions in the self-paced reading experiment. Numbers are the means and 95\,\% credible intervals. Blue vertical lines represent the median and shaded areas are 80\,\% intervals.}
    \label{fig:spr_posteriors}
    \centering
    \includegraphics[width=\textwidth]{images/posteriors_spr_pooled_774.png}
\end{figure}

Bayes factors, the Bayesian version of hypothesis testing, were used to evaluate whether there was evidence for the effects estimated above while taking into account the uncertainty \citep{schad_etal_2022_BF}. The Bayes factor analysis is presented in Figure \ref{fig:spr_bfs}. Bayes factors provided extremely strong evidence for the semantic interference effect in the pre-critical, critical and spill-over region (BF$_{10}$ > 200). Bayes factors showed no effect of syntactic interference in any of the investigated regions. In fact, the Bayes factor analysis actually provided evidence against the syntactic interference effect in all regions and under all priors (BF$_{10}$ < 1).  Evidence for the interaction was only found in the critical region, where it ranged from strong (BF$_{10}$ = 40) to weak (BF$_{10}$ = 2) depending on the a priori assumed effect size.

\begin{figure}[H]
    \caption{Bayes Factors for the effects of semantic interference, syntactic interference and their interaction in the reading times at the critical verb and surrounding regions.}
    \label{fig:spr_bfs}
    \centering
    \includegraphics[width=\textwidth]{images/BF_plot_spr_774_allregions.png}
\end{figure}

\section{Discussion}
We presented a large-sample self-paced reading study that investigated the use of syntactic and semantic features during subject-verb dependency formation. Comprehension accuracy and reading times of the critical verb showed semantic interference, but no syntactic interference. Importantly, in the reading times, the effect did not emerge at the critical verb, i.e., the retrieval site during subject-verb dependency formation, but actually started when the distractor was read.

\subsection{Pre-critical effects}
Animate distractors (high semantic interference) were read slower than inanimate distractors (low semantic interference, see Figure \ref{fig:whole_sentence} A and B). One might argue that this could be due to differences in word length. The animate distractors in our materials were on average 1.1 letters longer than the inanimate distractors (mean length of animate distractors: 9.3, sd: 2.6, mean length of inanimate distractors: 8.2, sd: 2.9). It seems unlikely that this small difference in word length caused such a large and long-lasting effect.

We assume that the semantic interference effect starting at the distractor and persisting into later regions was caused by encoding interference \citep{Oberauer_Kliegl_2006}. The increased effort of encoding and subsequently maintaining representations of three different animate noun phrases (the introduction noun, the subject and the animate distractor) caused the comprehender to slow down \citep[for similar findings, see e.g., ][]{lago_etal_2021, kush_etal_2015, gordon02}.

The pre-critical effects in the previous studies \citep{vandyke07, mertzen} might have also started at the distractor. \citeauthor{mertzen}'s (\citeyear{mertzen}) Figures 5 and 6 indicated reading time differences in earlier regions, especially for their German data (see their Figure 6). \citet{vandyke07} did not report reading times for the whole sentences / distractors. While \citet{vandyke07} assumed that the pre-critical effects were due to plausibility differences between conditions, \citet{mertzen} also discussed encoding interference as the cause of pre-critical effects in their study. Our results strongly support the encoding interference explanation because the effects started at the distractor.

Alternative causes of the pre-critical effects discussed by \citet{mertzen} are parafoveal-on-foveal effects, sentence structure confounds and prediction. Our study rules out the parafoveal-on-foveal explanation, because there is no parafoveal preview in self-paced reading. The observed difference between the high and low semantic interference conditions is independent of the syntactic manipulation. Therefore, the sentence structure confound is not a good explanation for the effect in our study. \citet{mertzen} argued that the pre-critical adverb is the first word of the verbal phrase and therefore, might trigger the retrieval of the subject. In our study, the effect started at the distractor and became smaller as the two pre-critical adverbs were read (see Figure \ref{fig:whole_sentence} A and B). Consequently, the prediction explanation is also ruled out by our findings, rendering the encoding interference explanation the most likely explanation of the effects found prior to the critical verb in our and previous studies. Crucially this line of reasoning should not be limited to the explanation of the pre-critical effects, but should be extended to the effects in the critical region as well. The reading times for high vs.\ low semantic interference conditions started to differ at the distractor and differed throughout the rest of the sentence. It is not possible to pinpoint whether the effect in the critical region is due to a retrieval initiated at this region or still due to encoding and maintaining the distractor in memory.

\subsection{Comparison with previous findings}
The results of the present study stand in contrast to previous findings \citep{vandyke07, mertzen}. The present study is the only one to find semantic and no syntactic interference effect. The difference in observed effects could be explained by differences in statistical power or by methodological differences. The present study has higher statistical power than the previous studies. \citet{vandyke07} had 35 - 40 participants and 36 - 48 items in each of her three experiments, respectively. \cite{mertzen} tested 61 English speakers and 121 German speakers with 40 items each. In contrast, we tested 774 participants with at least 60 items each (a subset of 160 participants read all 120 items). Therefore, the present study is the study with the highest power to date using this 2 $\times$ 2 interference design. Consequently, the estimates from the present study are the most precise estimates for this design. The small effect size in the present study is comparable to that of other large-scale studies \citep{nicenboim} and meta-analyses on interference \citep{jaeger_etal_2017}.

An obvious difference from previous studies is the experimental methodology. The majority of the previous experiments employed eye-tracking while reading methodology, while we used a self-paced reading task. The exact relation of reading times obtained by these two methods is unclear. Self-paced reading could facilitate interference effects compared to natural reading (as in eye-tracking studies) due to the restricted reading format. Comprehenders have no opportunity to revisit previous material during conventional self-paced reading  \citep[but see][]{BSPR}. This is more demanding on the comprehender's memory which might enhance interference effects. This argumentation is supported by our estimation of the results of \citeauthor{vandyke07}'s (\citeyear{vandyke07}) Experiment 1, the only other self-paced reading experiment using this design (see Figure \ref{fig:previous}). The estimates of both main effects (syntactic and semantic interference) and the interaction in the spill-over region are very similar to the results of the present study in the critical region. This similarity between the two self-paced reading experiments further validates the findings of the present study. But it remains unclear why semantic interference was especially prominent in our study compared to the previous ones.

The contrast between our results and the results from  \citeauthor{mertzen}'s (\citeyear{mertzen}) German experiment is surprising given that both used German items and partially even identical items. So, why did we find a semantic interference effect and \citet{mertzen} did not? This could be due to lower power in \citeauthor{mertzen}'s (\citeyear{mertzen}) study. While they already had considerably more participants and items than many psycholinguistic studies, in the present study the number of participants was much higher than in theirs (774 vs.\ 121) and the number of items was also higher (60/120 vs.\ 40). This is also supported by the reduced uncertainty of the individual-level estimates in our data compared to \citeauthor{mertzen}'s (\citeyear{mertzen}). We will discuss the lack of syntactic interference in our data in the general discussion.

>>>>

It is well-known \parencite[e.g., ][]{rayner2000effect} that the last word in a clause-final position causes a slowdown in reading; such a slowdown has the potential to spill over to the subsequent regions, possibly affecting the estimated effects at the pre-critical and critical regions. The spill-over of longer reading times can be problematic because the standard deviation increases as well \parencite{wagenmakers2007linear}; such an increase in standard deviation would drastically lower statistical power. In order to attenuate spill-over from the clause-final word in the embedded clause preceding the critical region, we inserted two adverbs. This way, the critical region will be less affected by the clause-boundary slowdown. This design also has the advantage that any potential effects seen at the pre-critical region (the adverb preceding the verb) are less likely to be due to spill-over; it is important to look at the pre-critical region as previous work with this design found effects at the pre-critical region (we revisit this detail in the General discussion).

@@

\subsubsection{Self-paced reading times (Experiments 1a and 1b combined)}

\paragraph{Estimated effect sizes and their uncertainty}

Reading times across the whole sentence are shown in Figure \ref{fig:whole_sentence} A and B, separately for high and low syntactic interference because these conditions had partially different sentence structures.

@@

It is apparent from Figure \ref{fig:whole_sentence} A and B that, regardless of the syntactic manipulation, at the distractor, reading times between high and low semantic interference started to differ: distractors in the high semantic interference conditions induced longer reading times than in the low semantic interference conditions. This pattern persisted in the following regions.

Because the distractor and the immediately following regions differ by condition, we did not compute Bayes factors for these differences. Instead we focused our Bayes factors analyses on regions which were identical across conditions. These are the pre-critical, critical and spill-over regions.

%This is probably due to encoding interference \citep{mertzen, jaeger_etal_2015_retrieval_encoding} and persisted in the following regions.

Figure \ref{fig:whole_sentence} C shows the reading times of these regions; here, we also show the pre-pre-critical region, which was identical across conditions as well, but will be harder to interpret because of possible spill-over from the syntactic manipulation. The pre-pre-critical and pre-critical region show longer reading times for high vs.\ low semantic interference conditions. The critical verb was read slowest when syntactic and semantic interference were both high and fastest when syntactic interference was high and semantic interference low. The other two conditions showed intermediate reading times. The spill-over region again primarily showed a difference between high and low semantic interference conditions.

Panel D shows the reading times of the critical and surrounding regions for each of the two Experimenta 1a and 1b separately. In Experiment 1a, the first session (items 1-60, N = 204, left most sub-figure) showed results similar to the pooled results presented in Panel C. In the second session of Experiment 1a (items 61-120, N = 160) a smaller semantic interference effect was seen at the critical verb and the patterns in the surrounding regions were less clear than in the first session. Additionally, the second session in Experiment 1b showed shorter reading times compared to the first session. As mentioned earlier, this attenuation in reading times and differences between conditions is likely due to  adaptation to the task in the second session.

Panel D also shows that Experiment 1b with items 1-60 (N = 350) showed a pattern consistent with   semantic interference in all regions. Experiment 1b with items 61-120 (N = 220, right most sub-figure) showed a pattern consistent with semantic interference in the regions surrounding the critical verb, but not at the verb itself. At the verb, reading times were longest when both syntactic and semantic interference were high. Reading times were a bit faster when both syntactic and semantic interference were low. The other two conditions (high syntactic/low semantic and low syntactic/high semantic) lead to the fastest verb reading times in Experiment 1b with items 61-120.

%These somewhat inconsistent results, especially in the critical region, across the sub-experiments and the random assignment of participants to the sub-experiments motivated us to gain estimates of the effects under investigation for the individual participants (see Figure \ref{fig:spr_individual}).

%\begin{figure}[H]
 %   \caption{Individual estimates of syntactic and semantic interference and their interaction at the critical verb for all 774 participants in the self-paced reading experiment. Shown are shrunken estimates from a Bayesian hierarchical linear mixed model. Circles show individual’s mean effects, errors bars are 95\,\% credible intervals. The red dashed line shows an effect of zero (difference of zero milliseconds). Two solid red lines mark an effect size of 10 and 20 ms, respectively.}
%    \label{fig:spr_individual}
 %   \centering
  %  \includegraphics[width=\textwidth]{images/individual_diffs.jpg}
%\end{figure}

%The individual-level effects were derived from a Bayesian linear mixed model with the priors shown in Table \ref{tab:spr_priors} with the intermediate slope prior of Normal(0, 0.05) and random slopes for syntactic and semantic interference and their interaction but without correlations of random effects.

%Figure \ref{fig:spr_individual} shows that at the critical verb, the 95\,\% credible intervals for the syntactic interference effect of all participants were centered around zero. In contrast, participants consistently displayed a small effect of semantic interference with narrow 95\,\% credible intervals. The individual-level estimates of the interaction were a bit larger but they were associated with more uncertainty (wider 95\,\% credible intervals). The individual-level results help to understand the population-level posteriors presented in Figure \ref{fig:spr_posteriors} and the population-level Bayes factor analysis (see Figure \ref{fig:spr_bfs}).

Turning now to the estimates of the main effects and interaction parameters in the pooled data (Experiments 1a and 1b combined), Figure \ref{fig:spr_posteriors} shows that the pre-critical, critical and spill-over regions showed very similar posterior distributions for the parameters. For syntactic interference, they were close to zero in all regions. In contrast, for semantic interference, the estimates ranged between [8,14] ms (pre-critical), [4, 12] ms (critical), and [5, 11] ms (spill-over region). The posteriors for the interaction were consistent with an interaction effect. The interaction was the  largest in the critical region ([7, 22 ms]).

\begin{figure}[H]
    \caption{Posteriors for the syntactic and semantic interference effects and their interaction at the critical verb and surrounding regions in the pooled self-paced reading data (Experiments 1a and 1b combined). The numerical values are the means and 95\,\% credible intervals. The blue vertical lines represent the median and the blue shaded areas are 80\,\% credible intervals.}
    \label{fig:spr_posteriors}
    \centering
    \includegraphics[width=\textwidth]{images/posteriors_spr_pooled_774.png}
\end{figure}

\paragraph{Hypothesis testing using Bayes factors}

Was there any evidence for the effects estimated above.  The Bayes factor analysis is presented in Figure \ref{fig:spr_bfs}. The analyses use all the data from Experiments 1a and 1b. We found extremely strong evidence for the semantic interference effect in the pre-critical, critical and spill-over regions (BF$_{10}$ > 200). No evidence was found for syntactic interference in any of the investigated regions; in fact, there is strong evidence against the syntactic interference effect in all regions and under all the priors used (BF$_{10}$ < 1).  Evidence for the interaction was only found in the critical region. Here, the evidence for the interaction was strong (BF$_{10}$ = 40) when the prior on the parameter was N+(0, 0.01), i.e., a small a priori effect size ranging from  [0, 8] ms; the evidence for the interaction was much weaker if the prior is N+(0,0.1), i.e., a larger a priori effect size ranging from [0, 81] ms. In other words, only if we assume a priori that the effect size for the interaction is relatively small, then there is strong evidence for this effect.

\begin{figure}[H]
    \caption{Bayes Factors for the effects of semantic interference, syntactic interference and their interaction in the reading times (combined Experiments 1a and 1b) at the critical verb and surrounding regions, under a range of priors on the target parameters.}
    \label{fig:spr_bfs}
    \centering
    \includegraphics[width=\textwidth]{images/BF_plot_spr_774_allregions.png}
\end{figure}

\section{Discussion}
We presented a large-sample self-paced reading study that investigated the use of syntactic and semantic features during subject-verb dependency formation. Reading times at the critical verb showed clear evidence for semantic interference, but evidence against syntactic interference. The semantic interference effect was already present at the pre-critical region; i.e., semantic interference occured even before the retrieval event could begin.

\subsection{The effects in the pre-critical region}

At the distractor (which occurred well before the pre-critical region), animate distractors (high semantic interference) were read slower than inanimate distractors (low semantic interference, see Figure \ref{fig:whole_sentence} A and B). One might argue that this pattern could be due to differences in word length. The animate distractors in our materials were on average 1.1 letters longer than the inanimate distractors (mean length of animate distractors: 9.3, sd: 2.6, mean length of inanimate distractors: 8.2, sd: 2.9). It seems unlikely that this small difference in word length caused such a large and long-lasting effects, but in order to be conservative we do not try to interpret this difference.

At the pre-critical region, there was clear evidence for semantic interference. As this cannot be due to retrieval interfernce, the most likely explanation is encoding interference \citep{Oberauer_Kliegl_2006}. The increased effort of encoding and subsequently maintaining representations of three different animate noun phrases (the introduction noun, the subject and the animate distractor) is the most likely reason for the slowdown in high vs.\ low semantic interference conditions \citep[for similar findings, see e.g., ][]{lago_etal_2021, kush_etal_2015, gordon02}.

Indeed, previous work using the same design as in the present paper has also found semantic interference effects at the pre-critical region: both \cite{vandyke07} and \cite{mertzen} found such effects. \citeauthor{mertzen}'s (\citeyear{mertzen}) Figures 5 and 6 indicated reading time differences in earlier regions, especially for their German data (see their Figure 6). \cite{vandyke07} did not report reading times for the whole sentences / distractors;  \citeauthor{vandyke07} attributed the effects observed at the pre-critical region to plausibility differences between conditions, but as \cite{mertzen} also points out, encoding interference could be an explanation even in that study. Given these earlier findings, our results are consistent with the encoding interference explanation.

\cite{mertzen} observed both syntactic and semantic interference effects in the pre-critical region. 
They discuss several alternative explanations for their observed effects. In addition to encoding interference, \cite{mertzen} propose three other alternative explanations for their data: parafoveal-on-foveal effects, sentence structure confounds across conditions, and predictive processing effects. Our results cannot be explained by the parafoveal-on-foveal explanation, because there is no parafoveal preview in self-paced reading. The observed difference between the high and low semantic interference conditions is independent of the syntactic manipulation. Therefore, the sentence structure confound is also not a good explanation for the effect in our study. Regarding the predictive-processing explanation, \citet{mertzen} argued that the pre-critical adverb must attach to the upcoming the verbal phrase; this leads to an anticipatory creation of a verb phrase chunk in memory, which triggers a retrieval of the subject already at the pre-critical region. However, in our study, the effect started at the distractor and became smaller as the two pre-critical adverbs were read (see Figure \ref{fig:whole_sentence} A and B). The predictive-processing explanation would incorrectly predict that the effect begins at the second adverb, which immediately precedes the verb. Consequently, the prediction explanation is also ruled out in our data, rendering encoding interference as the most likely explanation of the effects found prior to the critical verb in our data. Crucially this line of reasoning should not be limited to the explanation of the pre-critical effects, but should be extended to the effects in the critical region as well. The reading times for high vs.\ low semantic interference conditions started to differ at the distractor and differed throughout the rest of the sentence. It is not possible to pinpoint whether the effect in the critical region is due to a retrieval initiated at this region, or still due to encoding and maintaining the distractor in memory, or a combination of the two kinds of interference.

\subsection{Comparison with previous findings}
The results of the present study stand in contrast to previous findings \citep{vandyke07, mertzen}. The present study is the only one to find semantic and no syntactic interference effect. The difference in observed effects could be explained by differences in statistical power or by methodological differences. The present study has higher statistical power than the previous studies. \citet{vandyke07} had 35 - 40 participants and 36 - 48 items in each of her three experiments, respectively. \cite{mertzen} tested 61 English speakers and 121 German speakers with 40 items each. In contrast, we tested 774 participants with at least 60 items each (a subset of 160 participants read all 120 items). Therefore, the present study is the study with the highest power to date using this 2 $\times$ 2 interference design. Consequently, the estimates from the present study are the most precise ones so far for this design. The smaller effect size in the present study is a consequence of higher power, and the magnitude of the effects observed is comparable to that of other large-scale reading studies \citep{nicenboim} and meta-analyses on interference \citep{jaeger_etal_2017}.

An obvious difference from previous studies is the experimental methodology. The majority of the previous experiments employed eye-tracking while reading, while we used a self-paced reading task. Self-paced reading (SPR) could trigger a greater tendency to cause interference effects compared to natural reading (as in eye-tracking studies), due to the restricted reading format in SPR: Comprehenders have no opportunity to revisit previous material during conventional self-paced reading  \citep[but see][]{BSPR}. SPR is likely to be more demanding on the comprehender's memory, which might make it easier to detect interference effects. This argumentation is supported by our estimation of the results of \citeauthor{vandyke07}'s (\citeyear{vandyke07}) Experiment 1, the only other self-paced reading experiment using this design (see Figure \ref{fig:previous} in the appendix).  In the critical region, the estimates of both main effects (syntactic and semantic interference) are very similar to the results of the present study; the interaction effect observed by  \citeauthor{vandyke07} in the spill-over region is also similar to our estimate. However, it remains unclear why semantic interference was especially prominent in our study compared to the previous ones.

The contrast between our results and those from  \citeauthor{mertzen}'s (\citeyear{mertzen}) German experiment is surprising given that both used German items and partially even identical items. So, why did we find a semantic interference effect in all regions, whereas \citet{mertzen} only found one in the pre-critical region? One possible explanation is lower power in \citeauthor{mertzen}'s (\citeyear{mertzen}) study. While they already had considerably more participants and items than many psycholinguistic studies, in the present study the number of participants was much higher than in theirs (774 vs.\ 121) and the number of items was also higher (60/120 vs.\ 40). 
%This is also supported by the reduced uncertainty of the individual-level estimates in our data compared to \citeauthor{mertzen}'s (\citeyear{mertzen}). 
We will discuss the absence of syntactic interference in our data in the general discussion.
